---
title: "Tests"
output: html_document
date: "`r Sys.Date()`"
---

Surv_Pred must be able to :
 - read the existing survival database with treatment group based on that column with maximum complexity / combination.
 - extract data from existing survival database
 - create projections and use survplot to return them according to the desired factors
 
 
 Info table we need to extract information from surv_database as surv_db_ref,
 We need:
 
 What if first I make a curves extractor function from the surv_database, in which case we would need:
 - the database
 - the pathogen
 - the study.id of interest (%in%) 
 - the factors (column name and contents)

 So in this dataset, every row would represent a curve i guess. 
 
 So the function will be like:
 
 Surv_Select() #Surv select should also remove NA column contents I think. Basically this is equivalent to dplyr::semi_join() so we will use that instead. This will be quite convenient because then we can just semi_join() and select the correct groups. seems to work nicely with NA values (ignored). I mean at most we will have like 3-4 rows as the dataframe to reference as the filtering guide, so its not going to be too work intensive. Ok you know what I think I need to put semi_join inside Surv_Pred(). This is in order to also recognize the factors used and the relevant survival groups (per row of the semi_join guide data).
 
```{r}
 surv_db = survival::survSplit(surv_db_ex[surv_db_ex$TTE > 0,], cut = 37, end = "TTE", event = "Status", episode = "Obs")
 surv_db = surv_db[surv_db$Obs == 1,]
 ref_surv_db = surv_db_ex
 ref_surv_db$Study = sample(c("QCATC1068", "QCATC997"), replace = TRUE, size = 1200)
 ref_specs = data.frame(Study = "QCATC1068",
                        Trt.ID = "A",
                        TTE_offset = -2)
 pred_tte = 54
 phi = 1.5
 dailybin = TRUE
 lambda = NULL
 plot_save = TRUE
 plot_dim = c(7, 4.3)

Surv_Pred = function(surv_db,
                     ref_surv_db,
                     ref_specs,
                     pred_tte,
                     dailybin = TRUE,
                     phi = 1.5,
                     lambda = NULL,
                     plot_save = TRUE, #arguments to be passed to survplots?
                     plot_prefix = "ONDA_XX",
                     plot_dim = c(7, 4.3)){ #arguments to be passed to survplots

 surv_db_ref0 = merge(ref_surv_db, ref_specs)
 surv_db_ref0 = surv_db_ref0[!is.na(surv_db_ref0$TTE_offset),]
 if(nrow(surv_db_ref0) == 0) stop("No reference study selected. Possible ref_specs mismatch with ref_surv_db.")
 surv_db_ref0$TTE = surv_db_ref0$TTE + surv_db_ref0$TTE_offset
 surv_db_ref0$unique = interaction(surv_db_ref0$Study, surv_db_ref0$Trt.ID, sep = " ") |> trimws()
 
 #Enforce >0 TTEs
 surv_db_ref0 = surv_db_ref0[surv_db_ref0$TTE > 0, ]
 surv_db = surv_db[surv_db$TTE > 0, ]
 
 #Get reference level hazard curve
 surv_db_ref0$unique = paste("ref", surv_db_ref0$unique)
 surv_db_ref0$Trt.ID = paste("ref", surv_db_ref0$Trt.ID)

 #Initialize dataframes
 project_db = data.frame()
 end_db = data.frame()
 ref_haz = data.frame()
 ref_surv = data.frame()
 
 #For loop to predict based on the different reference groups in surv_db_ref.
 for(ref_unique in unique(surv_db_ref0$unique)){
   surv_db_ref = surv_db_ref0[surv_db_ref0$unique == ref_unique, ]

   #Print warning message if surv_db_ref end TTE < pred_tte
   if(max(surv_db_ref$TTE) < pred_tte) {
     warning(paste0("The desired 'pred_tte' (", pred_tte,
                   ") is greater than the maximum available in the reference database (",
                   max(surv_db_ref$TTE), ") - ", ref_unique, "."))
   }
   
   #Get ref_bshaz and ref_survfit
   tank_form = if(length(unique(surv_db_ref$Trt.ID)) == length(unique(surv_db_ref$Tank.ID))) "1" else "Tank.ID"
   ref_bshaz = silencer(bshazard::bshazard(data = surv_db_ref, as.formula(paste("survival::Surv(TTE, Status) ~", tank_form)),
                                           verbose = FALSE, phi = phi, lambda = lambda,
                                           nbin = if(dailybin == TRUE) max(surv_db_ref$TTE) else NULL))
   ref_haz = rbind(ref_haz, data.frame(ref_unique = sub("ref", "", ref_unique),
                                       hazard = ref_bshaz$hazard,
                                       time = ref_bshaz$time))
   ref_survfit = summary(survival::survfit(survival::Surv(TTE, Status) ~ 1, data = surv_db_ref))
   ref_surv = rbind(ref_surv, data.frame(ref_unique = sub("ref", "", ref_unique),
                                         surv = ref_survfit$surv,
                                         time = ref_survfit$time))
   
   #Check ref_bshaz
   if(any(diff(ref_bshaz$time) != 1)) stop("Incorrect time-interval in hazard dataframe. Please let Sean know!")
   
   #Loop for every treatment in the surv_db (not reference)
   for(pred_trt in levels(as.factor(surv_db$Trt.ID))) {

     #Combine reference and observed hazard dataframes
     surv_db_trt = surv_db[surv_db$Trt.ID == pred_trt,]
     comb_db = rbind(surv_db_ref[, c("Trt.ID", "Tank.ID", "TTE", "Status")], 
                     surv_db_trt[, c("Trt.ID", "Tank.ID", "TTE", "Status")])
     comb_db$Trt.ID = relevel(as.factor(comb_db$Trt.ID), ref = unique(surv_db_ref$Trt.ID))

     #Create cut_db
     cut_day = min(max(surv_db_trt$TTE), max(surv_db_ref$TTE))
     cut_db = survival::survSplit(comb_db, cut = cut_day, end = "TTE", event = "Status", episode = "Obs")
     precut_db = cut_db[cut_db$Obs == 1, ] #selecting phase 1 data only. Check if inclusive or not (desired = inclusive).
     precut_db$Tank.ID = interaction(precut_db$Tank.ID, precut_db$Trt.ID)

     #Precut_survfit and cumhaz
     precut_survfit = survival::survfit(survival::Surv(TTE, Status) ~ 1, data = surv_db_trt)
     precut_cumhaz = -log(tail(summary(precut_survfit)$surv, 1))

     #Precut_HR
     cox_mod = suppressWarnings(coxme::coxme(survival::Surv(TTE, Status) ~ Trt.ID + (1|Tank.ID),
                                              data = precut_db))
     pred_hr = exp(coef(cox_mod))

     #Postcut_bshaz
     postcut_timesFP = ref_bshaz$time > cut_day & ref_bshaz$time <= pred_tte
     postcut_haz = ref_bshaz$hazard[postcut_timesFP] * pred_hr
     postcut_cumhaz = if(length(postcut_haz) > 0) cumsum(postcut_haz) else 0
     postcut_times = ref_bshaz$time[postcut_timesFP]
     
     #Predict SRs
     project_temp = data.frame(ref_unique = sub("ref", "", ref_unique),
                               Trt.ID = pred_trt,
                               time = if(length(postcut_times) != 0) postcut_times else tail(ref_bshaz$time, 1),
                               hazard = if(length(postcut_haz) != 0) postcut_haz else tail(ref_bshaz$hazard, 1),
                               hr = pred_hr,
                               cumhaz = precut_cumhaz + postcut_cumhaz) |> suppressWarnings()
     project_temp$sr = exp(-project_temp$cumhaz)
     
     project_db = rbind(project_db, project_temp)
     end_db = rbind(end_db, project_temp[project_temp$time == tail(ref_bshaz$time, 1), -4])
     
   } #close loops by treatment in surv_db
  } #close loops by unique in ref_surv_db0

 linevec = c(2, 4, 1, 5, 6, 3)
 
 #Create projection plots
 sp = Surv_Plots(surv_db = surv_db,
                 lambda = lambda, phi = phi, dailybin = dailybin,
                 plot = "surv", plot_save = FALSE, xlim = c(0, pred_tte + 1))
 sp$layers[[1]]$mapping = aes(color = .data[["Trt.ID"]])
 sp$layers[[3]]$mapping = aes(color = .data[["Trt.ID"]]) 
 
 sp = suppressMessages({
   sp +
     geom_step(data = project_db, aes(x = ceiling(time), y = sr, color = Trt.ID, linetype = ref_unique), size = 0.8) +
     scale_linetype_manual(name = "Reference", values = linevec[1:length(unique(project_db$ref_unique))]) +
     scale_color_discrete(name = "Trt.ID") +
     guides(linetype = guide_legend(order = 1), colour = guide_legend(order = 2)) +
     geom_step(data = ref_surv, aes(x = time, y = surv, linetype = ref_unique), size = 0.8, color = "#6C6C6C", show.legend = FALSE) +
     theme(legend.key.width = unit(2, "lines"),
           plot.title = element_text(hjust = 0.5)) +
     ggtitle("Survival predictions based on past studies")
   })
 sp$layers = sp$layers[c(5, 1:4)]
 
 hp = suppressMessages({
   Surv_Plots(surv_db = surv_db,
                 lambda = lambda, phi = phi, dailybin = dailybin,
                 plot = "haz", plot_save = FALSE, xlim = c(0, pred_tte + 1)) +
     geom_line(data = project_db, aes(x = time, y = hazard, color = Trt.ID, linetype = ref_unique), size = 0.8) +
     geom_point(data = project_db, aes(x = time, y = hazard, color = Trt.ID)) +
     scale_linetype_manual(name = "Reference", values = linevec[1:length(unique(project_db$ref_unique))]) +
     scale_color_discrete(name = "Trt.ID") +
     scale_y_continuous(name = "Hazard") + 
     guides(linetype = guide_legend(order = 1), colour = guide_legend(order = 2)) +
     geom_line(data = ref_haz, aes(x = time, y = hazard, linetype = ref_unique), size = 0.8, 
               inherit.aes = FALSE, color = "#6C6C6C") +
     geom_point(data = ref_haz, aes(x = time, y = hazard), inherit.aes = FALSE, color = "#6C6C6C") +
     theme(legend.key.width = unit(2, "lines"),
           plot.title = element_text(hjust = 0.5)) +
     ggtitle("Hazard predictions based on past studies")
   })
 hp$layers = hp$layers[c(5:6, 1:4)]
 
 #Save plots
 if(plot_save == TRUE) {
   ggsave(plot = sp, filename = paste(plot_prefix, "Survival Projections.tiff"),
          dpi = 400, width = plot_dim[1], height = plot_dim[2])
   ggsave(plot = hp, filename = paste(plot_prefix, "Hazard Projections.tiff"),
          dpi = 400, width = plot_dim[1], height = plot_dim[2])
 }

 #Return Outputs
 output = list(Survival_Plot = sp,
               Hazard_Plot = hp,
               Predictions = project_db,
               End_Predictions = end_db)
 return(output)
}
```
```{r}
# In the first step, we load the reference database then specify the study and
# treatment to use as reference:
ref_surv_db = surv_db_ex
ref_specs = data.frame(Study = "QCATC1068",
                      Trt.ID = "A",
                      TTE_offset = 0)

 # Next, we load the ongoing study. Suppose it is mid-way to completion, hence the
 # survival data only extends to 35 TTE / DPC and we want to predict to 54. Lets
 # create the 35 TTE dataset for this demo:
 surv_db = survival::survSplit(data = surv_db[-1,], cut = 30, end = "TTE",
                               event = "Status", episode = "Eps")
 surv_db = surv_db[surv_db$Eps == 1, -c(3, 6)]
 tail(surv_db, n = 5)

 # Now chuck all the created objects into Surv_Pred()!
 Surv_Pred(surv_db = surv_db,
           ref_surv_db = ref_surv_db,
           ref_specs = ref_specs,
           pred_tte = 54)
```

