---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r}
library(safuncs)
library(ggplot2)

 # surv_db = survival::survSplit(surv_db_ex[surv_db_ex$TTE > 0,], cut = 37, end = "TTE", event = "Status", episode = "Obs")
 # surv_db = surv_db[surv_db$Obs == 1,]
 # ref_surv_db = surv_db_ex
 # ref_surv_db$Study = sample(c("QCATC1068", "QCATC997"), replace = TRUE, size = 1200)
 # ref_specs = data.frame(Study = "QCATC1068",
 #                        Trt.ID = "A",
 #                        TTE_offset = -2)


 phi = 1.5
 dailybin = TRUE
 lambda = NULL
 plot_dim = c(7, 4.3)
 factor = "Trt.ID"
 plot = "both"
 plot_prefix = "ONDA_XX"
 plot_lwrap = FALSE
 
surv_db = ongoing_surv_db
ref_surv_db = loocv_i$ref
ref_specs = loocv_i$ref_specs
pred_tte = max(loocv_i$ongoing$TTE)
plot_save = FALSE
 
 Surv_Pred = function(surv_db,
                     ref_surv_db,
                     ref_specs,
                     pred_tte,
                     dailybin = TRUE,
                     phi = 1.5,
                     lambda = NULL,
                     factor = "Trt.ID",
                     plot = "both",
                     plot_save = TRUE,
                     plot_prefix = "ONDA_XX",
                     plot_dim = c(7, 4.3),
                     plot_lwrap = FALSE){

  surv_db_ref0 = merge(ref_surv_db, ref_specs) #ref_specs[-"surv_db_Trt.ID"]
  surv_db_ref0 = surv_db_ref0[!is.na(surv_db_ref0$TTE_offset),]
  if(nrow(surv_db_ref0) == 0) stop("No reference study selected. Possible ref_specs mismatch with ref_surv_db.")
  surv_db_ref0$TTE = surv_db_ref0$TTE + surv_db_ref0$TTE_offset
  surv_db_ref0$unique = interaction(surv_db_ref0$Study, surv_db_ref0$Trt.ID, sep = " ") |> trimws()

  #Enforce >0 TTEs
  surv_db_ref0 = surv_db_ref0[surv_db_ref0$TTE > 0, ]
  surv_db = surv_db[surv_db$TTE > 0, ]

  #Get reference level hazard curve
  surv_db_ref0$unique = paste("ref", surv_db_ref0$unique)
  surv_db_ref0$Trt.ID = paste("ref", surv_db_ref0$Trt.ID)

  #Initialize dataframes
  project_db = data.frame()
  end_db = data.frame()
  ref_haz = data.frame()
  ref_surv = data.frame()

  #For loop to predict based on the different reference groups in surv_db_ref.
  for(ref_unique in unique(surv_db_ref0$unique)){
    surv_db_ref = surv_db_ref0[surv_db_ref0$unique == ref_unique, ]

    #Print warning message if surv_db_ref end TTE < pred_tte
    if(max(surv_db_ref$TTE) < pred_tte) {
      warning(paste0("The desired 'pred_tte' (", pred_tte,
                     ") is greater than the maximum available in the reference database (",
                     max(surv_db_ref$TTE), ") - ", ref_unique, "."))
    }

    #Get ref_bshaz and ref_survfit
    tank_form = if(length(unique(surv_db_ref$Trt.ID)) == length(unique(surv_db_ref$Tank.ID))) "1" else "Tank.ID"
    
    ref_bshaz = silencer(bshazard::bshazard(data = surv_db_ref, as.formula(paste("survival::Surv(TTE, Status) ~", tank_form)),
                                            verbose = FALSE, phi = phi, lambda = lambda,
                                            nbin = if(dailybin == TRUE) max(surv_db_ref$TTE) else NULL))
    ref_haz = rbind(ref_haz, data.frame(ref_unique = sub("ref", "", ref_unique),
                                        hazard = ref_bshaz$hazard,
                                        time = ref_bshaz$time))
    ref_survfit = summary(survival::survfit(survival::Surv(TTE, Status) ~ 1, data = surv_db_ref))
    ref_surv = rbind(ref_surv, data.frame(ref_unique = sub("ref", "", ref_unique),
                                          surv = ref_survfit$surv,
                                          time = ref_survfit$time))

    #Check ref_bshaz
    if(any(diff(ref_bshaz$time) != 1)) stop("Incorrect time-interval in hazard dataframe. Please let Sean know!")

    #Loop for every treatment in the surv_db (not reference)
    for(pred_trt in levels(as.factor(surv_db$Trt.ID))) {
      
      #Skip prediction if surv_db_Trt.ID not in ref_specs
      if("surv_db_Trt.ID" %in% colnames(ref_specs)) {
        if(ref_specs$surv_db_Trt.ID & sub("ref", "", unlist(strsplit(ref_unique, " ")))) next
      }

      #Combine reference and observed hazard dataframes
      surv_db_trt = surv_db[surv_db$Trt.ID == pred_trt,]
      comb_db = rbind(surv_db_ref[, c("Trt.ID", "Tank.ID", "TTE", "Status")],
                      surv_db_trt[, c("Trt.ID", "Tank.ID", "TTE", "Status")])
      comb_db$Trt.ID = relevel(as.factor(comb_db$Trt.ID), ref = unique(surv_db_ref$Trt.ID))

      #Create cut_db
      cut_day = min(max(surv_db_trt$TTE), max(surv_db_ref$TTE))
      cut_db = survival::survSplit(comb_db, cut = cut_day, end = "TTE", event = "Status", episode = "Obs")
      precut_db = cut_db[cut_db$Obs == 1, ] #selecting phase 1 data only. Check if inclusive or not (desired = inclusive).
      precut_db$Tank.ID = interaction(precut_db$Tank.ID, precut_db$Trt.ID)

      #Precut_survfit and cumhaz
      precut_survfit = survival::survfit(survival::Surv(TTE, Status) ~ 1, data = surv_db_trt)
      precut_cumhaz = -log(tail(summary(precut_survfit)$surv, 1))
      precut_cumhaz = if(length(precut_cumhaz) == 0) 0 else precut_cumhaz

      #Precut_HR
      cox_mod = suppressWarnings(coxme::coxme(survival::Surv(TTE, Status) ~ Trt.ID + (1|Tank.ID),
                                              data = precut_db))
      pred_hr = exp(coef(cox_mod))

      #Postcut_bshaz
      postcut_timesFP = ref_bshaz$time > cut_day & ref_bshaz$time <= pred_tte
      postcut_haz = ref_bshaz$hazard[postcut_timesFP] * pred_hr
      postcut_cumhaz = if(length(postcut_haz) > 0) cumsum(postcut_haz) else 0
      postcut_times = ref_bshaz$time[postcut_timesFP]

      #Predict SRs
      project_temp = data.frame(ref_unique = sub("ref", "", ref_unique),
                                Trt.ID = pred_trt,
                                time = if(length(postcut_times) != 0) postcut_times else tail(ref_bshaz$time, 1),
                                hazard = if(length(postcut_haz) != 0) postcut_haz else tail(ref_bshaz$hazard, 1),
                                hr = pred_hr,
                                cumhaz = precut_cumhaz + postcut_cumhaz) |> suppressWarnings()
      project_temp$sr = exp(-project_temp$cumhaz)

      project_db = rbind(project_db, project_temp)
      end_db = rbind(end_db, project_temp[project_temp$time == last(project_temp$time), -4])

    } #close loops by treatment in surv_db
  } #close loops by unique in ref_surv_db0

  linevec = c(2, 4, 1, 5, 6, 3)

  lwrap = function(x, plot_lwrap = FALSE) {
    out = if(plot_lwrap) sub(" ", ",\n", trimws(x)) else sub(" ", ", ", trimws(x))
    return(out)
  }

  if(plot %in% c("surv", "both")) {
    #Create projection plots
    sp = Surv_Plots(surv_db = surv_db, factor = factor,
                    lambda = lambda, phi = phi, dailybin = dailybin,
                    plot = "surv", plot_save = FALSE, xlim = c(0, pred_tte + 1))
    sp$layers[[1]]$mapping = aes(color = .data[["Trt.ID"]])
    sp$layers[[3]]$mapping = aes(color = .data[["Trt.ID"]])

    sp = suppressMessages({
      sp +
        geom_step(data = project_db, size = 0.8,
                  aes(x = ceiling(time), y = sr, color = Trt.ID, linetype = lwrap(ref_unique, plot_lwrap))) +
        scale_linetype_manual(name = "Reference", values = linevec[1:length(unique(project_db$ref_unique))]) +
        #guides(linetype = guide_legend(order = 1), colour = guide_legend(order = 2)) +
        geom_step(data = ref_surv, aes(x = time, y = surv, linetype = lwrap(ref_unique, plot_lwrap)),
                  size = 0.8, color = "#6C6C6C", show.legend = FALSE) +
        theme(legend.key.width = unit(1.5, "lines"),
              plot.title = element_text(hjust = 0.5))
      })
    sp$layers = sp$layers[c(5, 1:4)]
  }

  if(plot %in% c("haz", "both")){
    hp = suppressMessages({
      Surv_Plots(surv_db = surv_db, factor = factor,
                 lambda = lambda, phi = phi, dailybin = dailybin,
                 plot = "haz", plot_save = FALSE, xlim = c(0, pred_tte + 1)) +
        #guides(linetype = guide_legend(order = 1), color = guide_legend(order = 2)) +
        geom_line(data = project_db, linewidth = 0.8,
                  aes(x = time, y = hazard, color = Trt.ID, linetype = lwrap(ref_unique, plot_lwrap))) +
        geom_point(data = project_db, aes(x = time, y = hazard, color = Trt.ID)) +
        scale_linetype_manual(name = "Reference", values = linevec[1:length(unique(project_db$ref_unique))]) +
        scale_y_continuous(name = "Hazard") +
        geom_line(data = ref_haz, aes(x = time, y = hazard, linetype = lwrap(ref_unique, plot_lwrap)),
                  linewidth = 0.8, inherit.aes = FALSE, color = "#6C6C6C") +
        geom_point(data = ref_haz, aes(x = time, y = hazard), inherit.aes = FALSE, color = "#6C6C6C") +
        theme(legend.key.width = unit(1.5, "lines"),
              plot.title = element_text(hjust = 0.5))
    })
    hp$layers = hp$layers[c(5:6, 1:4)]
  }

  #Save plots
  if(plot_save == TRUE) {
    if(plot %in% c("surv", "both")){
      ggsave(plot = sp, filename = paste(plot_prefix, "Survival Projections.tiff"),
             dpi = 400, width = plot_dim[1], height = plot_dim[2])
    }
    if(plot %in% c("haz", "both")) {
      ggsave(plot = hp, filename = paste(plot_prefix, "Hazard Projections.tiff"),
             dpi = 400, width = plot_dim[1], height = plot_dim[2])
    }
  }

  #Return Outputs
  output = list(Survival_Plot = sp,
                Hazard_Plot = hp,
                Predictions = project_db,
                End_Predictions = end_db)
  
#print(output)
  return(output)
}
```
Surv_LOOCV() function. I think I need this to recognize pathogen?
```{r}
surv_db = ref_surv_db
ref_specs = ref_specs

Surv_LOOCV = function(surv_db,
                      ref_specs) {

  ref_specs_ori = ref_specs
  
  output = list()
  for(study_i in surv_db$Study){
    output[[study_i]]$ongoing = surv_db[surv_db$Study == study_i, ]
    output[[study_i]]$ref = surv_db[surv_db$Study != study_i, ]
    
    #recenter TTE_offset
    ref_specs$TTE_offset = ref_specs_ori$TTE_offset - ref_specs_ori$TTE_offset[ref_specs_ori$Study == study_i]
    
    output[[study_i]]$ref_specs = ref_specs[ref_specs$Study != study_i, ]
  }
  
  return(output)
}
```

Run Surv_Pred for every LOOCV
```{r}
#Can I make this a function?
Apply_SurvPred = function(loocv_list) {
  pred_results = list()
  for(loocv_name in names(loocv_list)) { #second layer for study, but I might need a first layer for pathogen..
    loocv_i = loocv_list[[loocv_name]]
    print(loocv_name)
    end_pred = data.frame()
    for(days_in in max(1, min(loocv_i$ongoing$TTE)): max(loocv_i$ongoing$TTE)) { #max(loocv_i$ongoing$TTE)
      
      ongoing_surv_db = survival::survSplit(loocv_i$ongoing[loocv_i$ongoing$TTE > 0,], cut = days_in, 
                                            end = "TTE", event = "Status", episode = "Obs")
      ongoing_surv_db = ongoing_surv_db[ongoing_surv_db$Obs == 1,]
    
      end_pred0 = Surv_Pred(surv_db = ongoing_surv_db,
                            ref_surv_db = loocv_i$ref,
                            ref_specs = loocv_i$ref_specs,
                            pred_tte = max(loocv_i$ongoing$TTE),
                            plot_save = FALSE)$End_Predictions |> suppressWarnings()
      
      if(nrow(end_pred0) > 0) {
        end_pred0$days_in = days_in
    
        #Put an averaging function here based on the different reference groups for a single Trt.ID?
        end_pred0 = end_pred0 |>
          dplyr::group_by(Trt.ID, days_in) |>
          dplyr::summarise(sr = mean(sr), time = mean(time)) |> suppressMessages() |> suppressWarnings()
        
        if(days_in == max(loocv_i$ongoing$TTE)) {
          end_pred0$true_end_sr = end_pred0$sr
          end_pred = merge(end_pred, end_pred0[, c("Trt.ID", "true_end_sr")])
        }
        
        end_pred = rbind(end_pred, end_pred0)
      }
      # Cleanup temporary files
      tmp_files = list.files(tempdir(), full.names = TRUE)
      unlink(tmp_files, recursive = TRUE, force = TRUE)
    }
    rownames(end_pred) = NULL
    pred_results[[loocv_name]] = end_pred
  }
  
  return(pred_results)
}
```

View predictions over time

```{r}
plot_type = 3
xlims = list("one-third" = c(34, 54), 
             "two-third" = c(44, 54))

Plot_Pred = function(pred_results, plot_type = 3, xlims, facet = FALSE) {

  #Make this whole thing a function (Pred_Diagnostics)? Only input variable probably the xlims.
  binded_res = dplyr::bind_rows(pred_results, .id = "Study")
  binded_res$group = interaction(binded_res$Study, binded_res$Trt.ID, sep = " ")
  binded_res$discrepancy = binded_res$sr - binded_res$true_end_sr
  
  if(facet == FALSE) {
    avg_db = binded_res |>
      dplyr::group_by(days_in) |>
      dplyr::summarise(avg_abs_disc = mean(abs(discrepancy)))
  } else {
    avg_db = binded_res |>
      dplyr::group_by(Study, days_in) |>
      dplyr::summarise(avg_abs_disc = mean(abs(discrepancy)))
  }
  
  plot_res = list()
  
  if(plot_type == 1){
    for(xlim in names(xlims)){
      plot_res[["plot_type1"]][[xlim]] = ggplot(data = binded_res, aes(x = days_in, y = sr, 
                                                                              group = group, color = Study)) +
      geom_step(alpha = 0.6) +
      scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
      geom_hline(data = binded_res,
                 aes(yintercept = true_end_sr, group = group, color = Study),
                 linetype = "dotted") +
      xlim(xlims[[xlim]]) +
      theme_bw()
      
      if(facet == TRUE) {
        plot_res[["plot_type1"]][[xlim]] = plot_res[["plot_type1"]][[xlim]] + facet_wrap(~Study)
      }
    }
  }
  
  if(plot_type == 2){
    for(xlim in names(xlims)){
      plot_res[["plot_type2"]][[xlim]] = ggplot(data = binded_res, aes(x = days_in, y = discrepancy, 
                                                                              group = group, color = Study)) +
        geom_step(alpha = 0.6) +
        scale_y_continuous(breaks = seq(-1, 1, 0.1), limits = c(-0.5, 0.5), oob = scales::squish) +
        scale_x_continuous(limits = xlims[[xlim]], n.breaks = 8) +
        theme_bw()
      
      if(facet == TRUE) {
        plot_res[["plot_type2"]][[xlim]] = plot_res[["plot_type2"]][[xlim]] + facet_wrap(~Study)
      }
    }
  }
  
  if(plot_type == 3){
    for(xlim in names(xlims)){
      plot_res[["plot_type3"]][[xlim]] = ggplot(data = binded_res, aes(x = days_in, y = abs(discrepancy), 
                                                                    group = group, color = Study)) +
        geom_step(alpha = 0.6) + 
        scale_y_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1), oob = scales::squish) +
        scale_x_continuous(limits = xlims[[xlim]], n.breaks = 8) +
        theme_bw() +
        geom_step(data = avg_db, aes(x = days_in, y = avg_abs_disc), color = "black", linewidth = 1, inherit.aes = FALSE)
      
      if(facet == TRUE) {
        plot_res[["plot_type3"]][[xlim]] = plot_res[["plot_type3"]][[xlim]] + facet_wrap(~Study)
      }
    }
  }
  
  return(plot_res)
}
```

Create LOOCV list
```{r}
ref_surv_db = read.csv(file = "Survival Data Library (updated 20Aug2025).csv")
#ref_surv_db = ref_surv_db[ref_surv_db$Pathogen == "M. viscosa",]
ref_surv_db = ref_surv_db[ref_surv_db$Pathogen == "Tenaci" & 
                            ref_surv_db$Pathogen.Strain != "T.maritimum" &
                            ref_surv_db$Study %in% c("QCATC1090", "QCATC1096-3", "QCATC997", "RD0051"), ]

#Moritella
# ref_specs = data.frame(Study = c("ONDA01166", "ONDA01254", "QCATC1090", "QCATC997"),
#                        Trt.ID = c("A (Control)", "A (Control)", 
#                                   "A (Ctrl Diet Unvac)", "E (Control)"),
#                        TTE_offset = c(-5, -2, 0, -8))
#A. sal
# ref_specs = data.frame(Study = c("ONDA01227-1", "ONDA01227-2"),
#                        Trt.ID = c("Group 2", "Control"),
#                        TTE_offset = c(0, 0))
#Y. ruckeri
# ref_specs = data.frame(Study = c("QCATC1070-1", "QCATC1078", "RD0028"),
#                        Trt.ID = c("Type2 3h-7", "Diet 1 (Control)", "Biotype 2 Med"),
#                        TTE_offset = c(0, -2, 0))
#P. sal
# ref_specs = data.frame(Study = c("QCATC1079", "RD0035"),
#                        Trt.ID = c("T1 (Control)", "2017_Current_25"),
#                        TTE_offset = c(-6, 0))
#ISAV
ref_specs = data.frame(Study = c("QCATC1090", "QCATC1096-3", "QCATC997", "RD0051"),
                       Trt.ID = c("F (Control)", "A (Control)", "50x - 20%T", "10^3 - 20%T"),
                       TTE_offset = c(-2, -3, 0, -2))

loocv_list0 = Surv_LOOCV(surv_db = ref_surv_db, #filter for the pathogen here. 
                        ref_specs = ref_specs)
```

Get Predicts
```{r}
pred_results0 = Apply_SurvPred(loocv_list0)
```

Get Plots
```{r}
xlims = list("one-third" = c(30, 55),
             "half-way" = c(34, 55))

#Using different references (peak)
# Plot_Pred(pred_results = pred_results1,
#           plot_type = 1, 
#           xlims = xlims,
#           facet = TRUE)
# 
# Plot_Pred(pred_results = pred_results1,
#           plot_type = 3, 
#           xlims = xlims,
#           facet = TRUE)

#Using  different references (flat)
# Plot_Pred(pred_results = pred_results2,
#           plot_type = 1,
#           xlims = xlims,
#           facet = TRUE)
# 
Plot_Pred(pred_results = pred_results0,
          plot_type = 1,
          xlims = xlims,
          facet = TRUE)
```

Using all data together
```{r}
# Plot_Pred(pred_results = pred_results0,
#           plot_type = 1, 
#           xlims = xlims,
#           facet = TRUE)

Plot_Pred(pred_results = pred_results0,
          plot_type = 3,
          xlims = xlims,
          facet = TRUE)
```

Step 1. Estimate tank variability on initial and final weights. 
Step 2. If tank variability is low, SGR variation between-tanks is probably caused entirely by fish-variability. 
Step 3. Estimate fish-variability in SGR at different size ranges. 

Use for power calculations (SGR). Can also be used for power calculation comparing final weight (FW). Weight gain (WG) also, but this is almost perfectly correlated with SGR p-values so its not something we should worry much about I think.
```{r}
library(dplyr)
library(lme4)
library(lmerTest)

sd_between_tanks = c()
  for(i in 1:1000){
  
  tank_num = 3
  trt_num = 1
  
  sim_db = data.frame()
  
  #Simulate data
  for(trt_i in 1:trt_num){
    for(tank_i in 1:tank_num){
      
      tank_val = rnorm(n = 1, mean = 0, sd = 0.039)
      fish_val = rnorm(n = 17, mean = 0, sd = 0.1053)
      y_val = tank_val + fish_val
      
      sim_db0 = data.frame(trt_id = LETTERS[trt_i],
                           tank_id = paste(LETTERS[trt_i], tank_i),
                           y_val = y_val)
      
      sim_db = rbind(sim_db, sim_db0)
    }
  }
  
  #Calculate tank averages
  avg_db = sim_db |>
    dplyr::group_by(tank_id) |>
    summarise(tank_avg = mean(y_val))

  sd_between_tanks = c(sd_between_tanks, sd(avg_db$tank_avg))
  }

mean(sd_between_tanks)
```

Final-tank weights inter-tank SD.
```{r}
tank_means = c()
for(tank_i in 1:10000) {
  sgr_coef = rnorm(n = 50, mean = log(717/245)/70, sd = 0.00127) + rnorm(n = 1, mean = 0, sd = 0.000365)
  Wf_sim = rnorm(n = 50, mean = 245, sd = 23.3) * exp(70 * sgr_coef)
  tank_means = c(tank_means, mean(Wf_sim))
}

sd(tank_means) #inter-tank SD estimated to be 16.9
```

Function to estimate inter-fish SD:
```{r}
estimate_fish_sgr_sd = function(Wi, #vector of initial weights
                                Wf, #vector of final weights
                                t,  #time between the two weights
                                sd_limits = c(0, 0.3), #x-axis range investigated
                                sd_increments = 0.002, #sds to be investigated
                                n_sim = 1000, 
                                show_plot = TRUE,
                                plot_title = "") {
  
  investigated_sds = seq(sd_limits[1], sd_limits[2], sd_increments)
  Wf_sim_mean_sds = c()
  
  sgr = (log(mean(Wf)) - log(mean(Wi))) / t
  target_sd = sd(Wf) 
  sd_attempts = investigated_sds / 100
  
  for(sd_i in sd_attempts){
    Wf_sim_sd = c()
  
    for(i in 1:n_sim){
      Wf_sim = Wi * exp(t * rnorm(n = length(Wi), mean = sgr, sd = sd_i))
      Wf_sim_sd = c(Wf_sim_sd, sd(Wf_sim))
    }
    Wf_sim_mean_sds = c(Wf_sim_mean_sds, mean(Wf_sim_sd))
  }
  
  if(show_plot == TRUE) {
    plot(y = abs(Wf_sim_mean_sds - target_sd), x = sd_attempts * 100, ylab = "Discrepancy", xlab = "SD used in simulation", 
         main = plot_title)
  }
  
  best_sd = sd_attempts[which(abs(Wf_sim_mean_sds - target_sd) == 
                                min(abs(Wf_sim_mean_sds - target_sd)))] #answer = 0.00108

  return(list = list("message" = paste("The best inter-fish SGR sd is estimated to be:", 100 * best_sd, "%BW/t"),
                     "value" = 100 * best_sd))
}
```

```{r}
VTW = read.csv(file = "VT Weights.csv")
results_compiled = data.frame()

for(trt_i in unique(VTW$Trt.ID)) {
  for(tank_i in unique(VTW$Tank.ID[VTW$Trt.ID == trt_i])) {
    
    fvtw = VTW[VTW$Tank.ID == tank_i & VTW$Trt.ID == trt_i, ] 
    res = estimate_fish_sgr_sd(Wi = fvtw$Weight[fvtw$Timepoint == "Initial"], 
                               Wf = fvtw$Weight[fvtw$Timepoint == "Final"], t = 168,
                               plot_title = paste0("Trt=", trt_i,", Tank=", tank_i))
    
    results_compiled = rbind(results_compiled, data.frame(trt_id = trt_i,
                                                          tank_id = tank_i,
                                                          fish_sd = res$value))
  }
}

results_compiled
```

Function to estimate inter-tank SD:
```{r}
estimate_tank_sgr_sd = function(fish_sd, fish_num, tank_num, observed_tank_sd,
                                sd_limits = c(0, 0.1), sd_increments = 0.001, n_sim = 1000,
                                plot_title = "", show_plot = TRUE) {
  
  investigated_sds = seq(sd_limits[1], sd_limits[2], sd_increments)
  sd_attempts = investigated_sds / 100
  tank_sd_at_each_attempt = c()
  
  tank_sd_at_each_attempt = c()
  for(sd_i in sd_attempts){
    tank_sds_i = c()
  
    for(iter in 1:n_sim) {
      tank_avweights = c()

      for(tank_i in 1:tank_num){
        tank_val = rnorm(n = 1, mean = 0, sd = sd_i)
        fish_val = rnorm(n = fish_num, mean = 0, sd = fish_sd / 100)
        y_val = tank_val + fish_val
        tank_avweights = c(tank_avweights, mean(y_val))
      }
      tank_sds_i = c(tank_sds_i, sd(tank_avweights))
    }
    
    tank_sd_at_each_attempt = c(tank_sd_at_each_attempt, mean(tank_sds_i))
  }
  
  discrepancy = abs(tank_sd_at_each_attempt - observed_tank_sd / 100)

  if(show_plot == TRUE) {
    plot(y = discrepancy, x = sd_attempts * 100, ylab = "Discrepancy", xlab = "Tank-SD used in simulation", 
         main = plot_title)
  }
  
  best_tank_sd = sd_attempts[which(discrepancy == min(discrepancy))] 
  
  return(list = list("message" = paste("The best inter-tank SGR sd is estimated to be:", 100 * best_tank_sd, "%BW/t"),
                     "value" = 100 * best_tank_sd))
}
```

```{r}
results_compiled$observed_tank_sd = 0.0415

tank_sd = c()
for(row_i in 1:nrow(results_compiled)){
  results_sel = results_compiled[row_i, ]
  
  tank_sd = c(tank_sd, 
              estimate_tank_sgr_sd(fish_sd = results_sel$fish_sd,
                                   fish_num = 17,
                                   tank_num = 3,
                                   observed_tank_sd = results_sel$observed_tank_sd,
                                   n_sim = 1000)$value)
  print(row_i)
}

results_compiled$tank_sd = tank_sd
results_compiled
```

