---
title: "Get Started!"
author: "Sean Andrew"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{safuncs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to the documentation of the R package `safuncs`! The package is designed to assist you in the analysis of your biological data (e.g. survival).

Below I wrote a short tutorial on how some of the core functions in `safuncs` can be used.

To get started, please install and load the package by running the following code:
```{r, results = "hide", message = FALSE, warning = FALSE}
remotes::install_github("sean4andrew/safuncs") #install package
library(safuncs) #load
```

## Survival Analysis

At ONDA, survival data is often available to scientists initially in the form of rows of entries for every mortality observed. This data needs to be converted to a useful form for analysis in R or Prism. The function `Surv_Gen()` shortens the data transformation step to just one line of code! Below, I show how to use them.

[Sean is procrastinating! Slap him to get his documentation done..]
