---
title: "Get Started!"
author: "Sean Andrew"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{safuncs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to the documentation of the R package `safuncs`! The package is designed to assist you in the analysis of your biological data (e.g. survival).

Below I wrote a short tutorial on how some of the core functions in `safuncs` can be used.

To get started, please install and load the package by running the following code:
```{r, results = "hide", message = FALSE, warning = FALSE}
remotes::install_github("sean4andrew/safuncs") # install package
library(safuncs) # load
```

## Survival Analysis

At ONDA, survival data is often available to scientists initially in the form of rows of entries for every mortality observed. This data needs to be converted to a useful form for analysis in R or Prism. The function `Surv_Gen()` shortens the data transformation step to just one line of code! Below, I showcase its use.

Let us first examine the raw survival data we can get from our OneDrive mort excel file: 
```{r}
data(mort_db_ex) # load example data file
head(mort_db_ex, n = 5) # view first 5 rows of data
```
The data contains several rows (first 5 shown) with each representing one mortality. The 2nd leftmost column indicates the Time to Event (TTE), e.g. days post challenge, and the last column indicates the type or Status of the event (1 = death, 0 = sampled-out or survived). Missing from this data are rows representing surviving fish (Status = 0); these needs to be present for a proper survival analysis.
<br>
<br>
Introducing `Surv_Gen()`!

Obtain the proper survival data by simply inserting the mort data into `Surv_Gen()`. Provide a time (TTE) indicating until when other fish survived and the starting number of fish used per tank.
```{r, results = "hide"}
Surv_Gen(mort_db = mort_db_ex,
         starting_fish_count = 100, # per tank
         last_tte = 54)
```

Below is the bottom 5 rows of the output dataframe, which shows some of the generated survivor data (note: Status = 0 for survivors)
```{r, echo = FALSE}
tail(Surv_Gen(mort_db = mort_db_ex,
              starting_fish_count = 100, # per tank
              last_tte = 54), n = 5)
```

You can also specify tank-specific fish numbers by inserting a dataframe as input to `starting_fish_count`!
```{r, eval = FALSE}
# reduce example data to simplify the demonstration
mort_db_ex2 = mort_db_ex[mort_db_ex$Tank.ID %in% c("C01", "C02", "C03"),]

# apply Surv_Gen()!
Surv_Gen(mort_db = mort_db_ex2,
         starting_fish_count = data.frame(Trt.ID = c("B", "A", "C"), # a vector of treatment groups for the specified tanks
                                          Tank.ID = c("C1", "C2", "C3"), # a vector with ALL tanks in the study
                                          starting_fish_count = c(100, 100, 50)), # a vector of fish numbers in same order as Tank.IDs
         last_tte = 54)
```

With your newly set up R script, you can now quickly regenerate survival data whenever there is a slight change in the mort database; perhaps from day-to-day or after corrections.

###################################################################
[Sean is procrastinating! Slap him to get this documentation done..]
