---
title: "Get Started!"
author: "Sean Andrew"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{safuncs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to the documentation of the R package `safuncs`! This package is designed to assist you in the analysis of your biological data (e.g. survival).

Below I wrote a short tutorial on how some of the core functions in `safuncs` can be used.

To get started, please install and load the package by running the following code:
```{r, results = "hide", message = FALSE, warning = FALSE}
remotes::install_github("sean4andrew/safuncs") # install package
library(safuncs) # load
```

## Survival Analysis

At ONDA, survival data is often available to scientists initially in the form of rows of entries for every mortality observed. This data needs to be converted to a useful form for analysis in R or Prism. The function `Surv_Gen()` shortens the data transformation step to just one line of code! Below, I showcase its use.

Let us first examine the raw survival data we can get from our OneDrive mort excel file: 
```{r}
data(mort_db_ex) # load example data file
head(mort_db_ex, n = 5) # view first 5 rows of data
```
The 2nd-leftmost column named *TTE* indicates the Time to Event, e.g. days post challenge, and the last column *Status* indicates the type of event (1 = death, 0 = sampled-out or survived). Missing from such a dataset are the rows representing surviving fish (Status = 0); these needs to be present for a proper survival analysis.
<br>
<br>
Introducing `Surv_Gen()`!

Obtain the proper survival data by simply inserting the mort database into `Surv_Gen()`. Provide a time (TTE) indicating until when other fish survived and the starting number of fish used per tank.
```{r, results = "hide"}
Surv_Gen(mort_db = mort_db_ex,
         starting_fish_count = 100, # per tank
         last_tte = 54)
```

Below is the output data's bottom 5 rows which represent the generated survivors (Status = 0).
```{r, echo = FALSE}
tail(Surv_Gen(mort_db = mort_db_ex,
              starting_fish_count = 100, # per tank
              last_tte = 54), n = 5)
```

You can also specify tank-specific starting fish numbers using a dataframe as input to `starting_fish_count`!
```{r, eval = FALSE}
# reduce example data to simplify the demonstration
mort_db_ex2 = mort_db_ex[mort_db_ex$Tank.ID %in% c("C01", "C02", "C03"),]

# apply Surv_Gen()!
Surv_Gen(mort_db = mort_db_ex2,
         starting_fish_count = data.frame(Trt.ID = c("B", "A", "C"), # a vector of treatment groups for the specified tanks
                                          Tank.ID = c("C1", "C2", "C3"), # a vector with ALL tanks in the study
                                          starting_fish_count = c(100, 100, 50)), # a vector of fish numbers in same order as Tank.IDs
         last_tte = 54)
```

With a short R script as shown, you can quickly regenerate survival data whenever there is a slight change in the mort database; perhaps from day-to-day or after corrections. 

For those wanting to use the generated survival data in prism, set the argument `output_prism = TRUE` in `Surv_Gen()` to save a prism-ready csv. in your working directory. If you want starting and ending dates in the Prism output, input a starting date into the argument `output_prism_date`, as shown:
```{r, results = "hide"}
Surv_Gen(mort_db = mort_db_ex,
         starting_fish_count = 100, # per tank
         last_tte = 54,
         output_prism = TRUE,
         output_prism_date = "08Aug2024")
```
<br>
<br>
Once the complete survival data has been obtained, plots can be easily generated using `Surv_Plots()`!
```{r, out.width = '100%'}
data(surv_db_ex) # load example complete survival data

Surv_Plots(surv_db_ex)
```
The plots save automatically to your working directory as a .tiff and in a power-point editable format (.pptx). Notably, `Surv_Plots()` accepts many more arguments that can influence the hazard plot in particular and needs tailoring for your specific experiment. For more details on these arguments, please see the functions' [documentation page](https://sean4andrew.github.io/safuncs/reference/Surv_Plots.html).

############TO BE CONTINUED###########
