---
title: "Get Started!"
author: "Sean Andrew"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{safuncs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to the documentation of package `safuncs`! It is designed to assist you in the analysis of your biological data (e.g. survival).

Below I wrote a short tutorial on how some of the core functions in `safuncs` can be used.

To get started, please install and load the package by running the following code:
```{r, results = "hide", message = FALSE, warning = FALSE}
remotes::install_github("sean4andrew/safuncs") #install package
library(safuncs) #load
```

## Survival Analysis

At ONDA, survival data is often readily available to the scientist in the form of rows of entries for every mortality observed. This dataset needs to be converted to a useful form for analysis in R or Prism. The functions `Surv_Gen()` and `Surv_Gen_Prism()` shortens the data transformation process to just one line of code! Below, I show how to use them.

[Sean is procrastinating! Slap him to get this documentation continued..]
